---
title: "homeworkdocu"
author: "jiangmengli19"
date: "2019-10-18"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction
Firstly, we download a set of data from the website
```{r importdataset}
library(RCurl)
download <- getURL("https://people.sc.fsu.edu/~jburkardt/data/csv/biostats.csv")
biostatsdata <- read.csv(text = download)
View(biostatsdata)

```

Secondly, We try to describe the data generally and choose "Height" and "Weight" column
to give some description in detail

```{r generaldescription}
summary(biostatsdata)
```
This is General descriptive statistic for the dataset. We can see the Mean of the height is 69.06 inch while the mean of the weight is 146.7lbs. This is a survey for the group of people aged between 23 years old and 53 years old.

Now we try to make a plot to show the relationship between Height and Weight generally
```{r plot}
plot(biostatsdata$Height..in.,biostatsdata$Weight..lbs.,xlab = "Height",ylab = "Weight")
```

Generally we can see there is some relation between two factors

